### 2015-04-03 LaTeX/skewnormal.tex
updates to the manuscript

\subsection{Extremal dependence}
Our interest lies in spatial dependence in the tail of the skew-$t$ process.
One measure of extremal dependence is the $\chi$ statistic \citep{Padoan2011}.
For a stationary and isotropic spatial process, the $\chi$ coefficient for two location $\bs$ and $\bt$ separated by distance $h = || \bs - \bt ||$ is
\begin{align}
  \chi(h) = \lim_{c \rightarrow \infty} \Pr[Y(\bs) > c | Y(\bt) > c].
\end{align}
If $\chi(h) = 0$, then observations are asymptotically independent at distance $h$.
For Gaussian processes, $\chi(h) = 0$ regardless of the distance, so they are not suitable for modeling spatially-dependent extremes.
Unlike the Gaussian process, the skew-$t$ process is asymptotically dependent.
However, one problem with the spatial skew-$t$ process is that $\lim_{h \rightarrow \infty} \chi(h) > 0$.
This occurs because all observations, both near and far, share the same $z$ and $\sigma$ terms.
Therefore, this long-range dependence feature of the skew-$t$ process is not ideal for spatial analysis of large geographic regions where we expect only local spatial dependence.
The explicit expression for $\chi(h)$ \citep{Padoan2011} and a proof of this are given in Appendix \ref{a:skewt}.

@@

\subsection{Censoring to focus on the tails}
To avoid bias in estimating tail parameters, we model censored data.
Let
\beq\label{Yt}
  \tilde{Y}(\bs) = \left\{ \begin{array}{ll}
      Y(\bs) \quad & \delta(\bs) = 1 \\
      T & \delta(\bs) = 0
  \end{array} \right.
\eeq
be the censored observation at site $\bs$ where $Y(\bs)$ is the uncensored observation, $\delta(\bs) = I[Y(\bs) > T]$, and $T$ is a pre-specified threshold value.
Then, assuming the uncensored data $Y(\bs)$ are observations from a skew-$t$ process, we update values censored below the threshold using standard Bayesian missing data methods as described in Section \ref{s:comp}.

\subsection{Partitioning to remove long-range asymptotic dependence}\label{s:part}
We handle the problem of long-range asymptotic dependence with a random partition model.
As discussed in Section \ref{s:spatialskew}, the source of long-range dependence is the shared $z$ and $\sigma$.
Therefore, to alleviate this dependence, we allow $z$ and $\sigma$ to vary by site.
The model becomes
\begin{align} \label{eq:partition}
  Y(\bs) &= \bX(\bs)^T \bbeta + \lambda \sigma(\bs) |z(\bs)| + \sigma(\bs) v(\bs).
\end{align}
Let $\bw = (w_1, w_2)$ be the location of a spatial knot.
To model spatial variation, consider a set of spatial knots $\bw_1, \ldots, \bw_K$ from a homogeneous Poisson process with intensity $\mu$ over spatial domain $\calD \in \calR^2$.
The knots define a random partition of $\calD$ by subregions $P_{1}, \ldots, P_{K}$ defined as
\begin{align} \label{eq:subregions}
  P_{k} = \{ \bs : k = \argmin_\ell || \bs - \bw_{\ell} || \}.
\end{align}
All $z(\bs)$ and $\sigma(\bs)$ for sites in subregion $k$ are assigned common values
\begin{align}
  z(\bs) &= z_{k} \label{eq:sitez}\\
  \sigma(\bs) &= \sigma_{k} \label{eq:sitesig},
\end{align}
and the $z_k$ and $\sigma^2_k$ are distributed as $z_k \iid N(0, 1)$ and $\sigma^2 \iid$ IG$(a, b)$.
So, within each partition, $Y(\bs)$ follows the spatial skew-$t$ process defined in Section \ref{s:spatialskew}.
Across partitions, the $Y(\bs)$ remain correlated via the correlation function for $v(\bs)$ because $v(\bs)$ spans all partitions.

When incorporating the random daily partition, conditional on knots $\bw_1, \ldots, \bw_K$, the $\chi$ statistic for two sites $\bs$ and $\bt$ in partitions $k_s$ and $k_t$ respectively is
\begin{align}
  \chi(h) &= I(k_s = k_t) \chi_{\text{skew-}t}(h) + I(k_s \neq k_t) \chi_{\text{Gaus}}(h) \nonumber \\
         &= I(k_s = k_t) \chi_{\text{skew-}t}(h)
\end{align}
where $I(\cdot)$ is an indicator function, $\chi_{\text{skew-}t}(h)$ is the $\chi$ statistic for a skew-$t$ process, $\chi_{\text{Gaus}}(h)$ is the $\chi$ statistic for a Gaussian process, and $h = ||\bs - \bt||$.
Therefore, sites in different subregions are asymptotically independent because $\chi_{\text{Gaus}}(h) = 0$ for all $h$.
Marginally, over the knots $\bw_1, \ldots, \bw_K$, $\chi(h) = \pi(h) \chi_{\text{skew}-t}(h)$, where $\pi(h) = \Pr(k_s = k_t)$ is the probability that two sites separated by distance $h$ are in the same partition.
So, to show that $\lim_{h \rightarrow \infty} \chi(h) = 0$, we need only know that $\lim_{h \rightarrow \infty} \pi(h) = 0$. A proof of this is given in Appendix \ref{a:proofsamepartition}.

In Figure \ref{fig:chi}, we give $\chi(h)$ for $K = 1, 3, 5, 10$ partitions for a skew-$t$ distribution with $\alpha = 10$, and $\nu = 3$ of freedom.
To estimate $\pi(h)$, we generate 500 sites uniformly over the unit-square.
We then randomly generate 400 different sets of partitions using $K = 3$, $5$, and $10$.
For each set of knots, we take $\pi(h)$ to be the proportion of sites in the same partition that are separated by distance $h$.

@@

We use an AR(1) time series model for $w_{tk}$, $z_{tk}$, and $\sigma_{tk}$.
The time series model must be specified after a transformation to preserve the skew-$t$ process at each time point.
For each time-varying parameter, we transform to obtain a standard normal marginal distribution, place a Gaussian prior with autocorrelation of the transformed parameter, and then transform back to obtain the marginal distribution required to preserve the skew-$t$ process.
We first transform the spatial knots from $\calD$ to $\calR^2$ as follows.
Let
\begin{align}
  w^*_{tki} = \Phi^{-1}\left[ \frac{ w_{tki} - \min(\bs_i)}{ \max(\bs_i) - \min(\bs_i) } \right], \quad i = 1, 2
\end{align}
where $\Phi$ is a univariate standard normal density function, and $\bs_i = [s_{1i}, \ldots, s_{ni}]$.
Then the transformed knots $\bw^*_{tk} \in \calR^2$.
We use a copula on $\sigma^2_t(\bs)$ to ensure that the marginal distributions of $\sigma^2_t(\bs)$ are inverse gamma.
Let
\begin{align}
  \sigma^{2*}_t(\bs) =\Phi^{-1}\left\{ \text{IG}[\sigma^2_t(\bs)] \right\}
\end{align}
where IG is the distribution function of an inverse gamma random variable.
We also use a copula on $z_{t}(\bs)$ to ensure that the marginal distributions of $z_t(\bs)$ are half-normal.
Let
\begin{align}
  z^*_t(\bs) = \Phi^{-1}\left\{ \text{HN}[\sigma^2_t(\bs)] \right\}
\end{align}
The AR(1) process for each tail parameter is $\bw^*_{1k} \sim N_w(0, 1)$, $z^*_{1k} \sim N(0, \sigma^2_{1k})$, $\sigma^{2*}_{1k} \sim N(0, 1)$, and for $t > 1$ the time series is modeled as
\begin{align}
  \bw^*_{tk} | \bw^*_{t-1, k} &\sim N_2\left[\phi_w \bw^*_{t-1, k}, (1 - \phi_w^2) \right] \\
  z^*_{tk} | z^*_{t-1, k} &\sim N \left[\phi_z z^*_{t-1, k}, \sigma^2_{tk} (1 - \phi_z^2)\right] \\
  \sigma^{2*}_{tk} | \sigma^{2*}_{t-1, k} &\sim N \left[\phi_\sigma \sigma^{2*}_{t-1, k}, (1 - \phi_\sigma^2) \right]
\end{align}
where $|\phi_w|$, $|\phi_z|$, $|\phi_\sigma| < 1$.
These are stationary time series models with marginal distributions $\bw^*_{k} \sim N_2(0, 1)$, $z^*_{k} \sim N(0, \sigma^2_{k})$, $\sigma^{2*}_{k} \sim N(0, 1)$.
After transformation back to the original space, $\bw_{tk} \sim \text{Unif}(\calD)$, $z_{tk} \sim HN(0, \sigma^2_{tk})$ $\sigma^2_{tk} \sim \text{IG}(a, b)$.
For each day, the model is identical to the spatial-only model in (\ref{eq:partition}) by construction.

\section{Computation}\label{s:comp}
First, we impute values below the threshold.
Then, we update $\Theta$ using Metropolis Hastings or Gibbs sampling when appropriate.
Finally, we make spatial predictions using conditional multivariate normal results and the fact that the distribution of $Y_t(\bs) \mid \Theta, z(\bs)$ is the usual multivariate normal distribution with a \Matern spatial covariance structure.

We can use Gibbs sampling to update $Y_t(\bs)$ for censored observations that are below the threshold $T$.
After conditioning on $\lambda$, $z_t(\bs)$ and non-censored observations, $Y_t(\bs)$ has truncated normal full conditionals.
So we sample $Y_t(\bs) \sim N_{(-\infty, T)}(\bX \bbeta, \bSigma)$.
After imputing the censored observations, we update the model parameters.
To update the model parameters, we use standard Gibbs updates for parameters when possible.
In the case Gibbs sampling is not possible, parameters are updated using a random-walk Metropolis Hastings algorithm.
See Appendices A.1 and A.2 for details regarding the MCMC.
The final step of the computation is to use Bayesian Kriging to generate a predictive distribution for $Y_t(\bs^*)$ at prediction location $\bs^*$.
This step is similar to the imputation for censored observations except that the full conditionals are no longer truncated at $T$.

\subsection{Hierarchical model}\label{s:hier}
Conditioned on $z_{tk}(\bs)$, $\sigma^2_{tk}(\bs)$, and $P_{tk}$, the marginal distributions are Gaussian and the joint distribution multivariate Gaussian.
However, we do not fix the partitions, they are treated as unknown and updated in the MCMC.
We model this with a Bayesian hierarchical model as follows.
Let $\bw_{t1}, \ldots, \bw_{tK}$ be a set of daily spatial knots in a spatial domain of interest, $\calD$, and $P_{tk}$ as defined in (\ref{eq:subregions}).
Then
\begin{align}
   Y_t(\bs) \mid z_{t}(\bs), \sigma^2(\bs), P_{tk}, \alpha, \beta, \Theta &= \bX_t(\bs)^T \beta + \lambda |z_t(\bs)| + \sigma_t(\bs) v_t(\bs) \label{eq:hier}\\
   z_t(\bs) &= z_{tk} \text{ if } \bs \in P_{tk}\nonumber\\
   \sigma^2_{t}(\bs) &= \sigma^2_{tk} \text{ if } \bs \in P_{tk}\nonumber\\
   \lambda &= \lambda_1 \lambda_2\nonumber\\
   \lambda_1 &= \left\{ \begin{array}{ll}
      +1 \quad & \text{w.p.} 0.5\\
      -1 \quad & \text{w.p.} 0.5
   \end{array}\right.\nonumber\\
   \lambda^2_2 & \sim IG(a, b)\nonumber\\
   v_t(\bs) \mid \Theta &\sim \Matern(0, \Sigma)\nonumber\\
   z^*_{tk} \mid z^*_{t-1, k}, \sigma^2_{tk} &\sim N(\phi_z z^*_{t-1, k}, \sigma^2_{tk} (1 - \phi_z^2))\nonumber\\
   \sigma^{2*}_{tk} \mid \sigma^{2*}_{t-1, k} &\sim N(\phi_\sigma \sigma^{2*}_{t-1, k}, (1 - \phi_\sigma^2))\nonumber\\
   \bw^*_{tk} \mid \bw^*_{t-1, k} &\sim N_2(\phi_w \bw^*_{t-1, k}, (1 - \phi_w^2)) \nonumber
\end{align}
where $\Theta = \{\rho, \nu, \gamma\}$, and $\Sigma$ is a \Matern covariance matrix as described in Section \ref{s:skewt}.
We parameterize $\lambda = \lambda_1 \lambda_2$ to help with convergence in the MCMC.

@@

\subsection{Design}\label{s:simdesign}
For all simulation designs, we generate data from the model in Section \ref{s:part} using $n_s=144$ sites and $n_t=50$ independent days.
The sites are generated Uniform$([0, 10] \times [0, 10])$.
We generate data from 7 different simulation designs:
\begin{enumerate} \setlength{\itemsep}{-0.5em}
  \item Gaussian marginal, $K=1$ knot
  % \item Symmetric-$t$ marginal, $K=1$ knot
  % \item Symmetric-$t$ marginal, $K=5$ knots
  \item Skew-$t$ marginal, $K=1$ knots
  \item Skew-$t$ marginal, $K=5$ knots
  \item Max-stable
  \item Transformation below $T = q(0.80)$
\end{enumerate}
In the first three designs, the $v_t(\bs)$ terms are generated using a \Matern covariance with smoothness parameter $\nu = 0.5$ and spatial range $\rho = 1$.
For the covariance matrices in designs 1 -- 3, the proportion of the variance accounted for by the spatial variation is $\gamma = 0.9$ while the proportion of the variance accounted for by the nugget effect is $0.1$.
In the first design, $\sigma^2 = 2$ is used for all days which results in a Gaussian distribution.
For designs 2 and 3, $\sigma^2_{tk} \iid \text{IG}(3, 8)$
For designs 1, we set $\lambda = 0$.
For designs 2 and 3, $\lambda = 3$ was used as to simulate moderate skewness, and the $z_t$ are generated as described in (\ref{eq:sitez}).
In the fourth design, we generate from a spatial max-stable distribution \citep{Reich2012}.
In this design, data have marginal distributions that follow a generalized extreme value distribution with parameters $\mu = 1, \sigma=1, \xi=0.2$.
In this model, a random effect is used to induce spatial dependence using 144 spatial knots on a regular lattice in the square $[1, 9] \times [1, 9]$.
For this setting, we set $\gamma = 0.5$.
In the final design, we generate $\tilde{y}$ using the setting from design two, and then consider the data
\begin{align}
  y = \left\{ \begin{array}{lc}
    \tilde{y}, \quad & \tilde{y} > T \\[0.5em]
    T \exp\{\tilde{y} - T\}, \quad & \tilde{y} \le T
  \end{array}\right.
\end{align}
where $T = q(0.80)$ is the 80th sample quantile of the data.
In all five designs, the mean $\bX^T \bbeta = 10$ is assumed to be constant across space.

$M = 50$ data sets are generated for each design.
For each data set we fit the data using five models
\begin{enumerate} \setlength{\itemsep}{-0.5em}
  \item Gaussian marginal, $K=1$ knots
  \item Skew-$t$ marginal, $K=1$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=1$ knots, $T=q(0.80)$
  \item Skew-$t$ marginal, $K=5$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=5$ knots, $T=q(0.80)$
\end{enumerate}
where $q(0.80)$ is the 80th sample quantile of the data.
The design matrix $\bX$ includes an the intercept with a prior of $\beta \sim \text{N}(0, 10)$.
The spatial covariance parameters have priors $\log(\nu) \sim \text{N}(-1.2, 1)$, $\gamma \sim \text{Unif}(0, 1)$, $\rho \sim \text{Unif}(15)$.
The skewness parameter has prior $\lambda \sim \text{N}(0, 2)$.
The residual variance terms have priors $\sigma^2_t(\bs) \sim \text{IG}(0.1, 0.1)$.
The knots have priors $\bw \sim \text{Unif}(\calD)$.
We do not include skewness for the thresholded models because it cannot be identified with only one tail worth of data, and we do not fit the data using the max-stable methods from \citet{Reich2012} because of the computational constraints.
Each chain of the mcmc ran for 20000 iterations with a burn-in period of 10000 iterations.
Parameters appear to converge properly; however, in the models with multiple partitions (i.e.models 4 and 5) it is hard to assess the convergence of $\bw$, $z(\bs)$, and $\sigma^2(\bs)$ because of partition label switching throughout the MCMC.

@@

Figure \ref{fig:simbrierscores} shows that when the data come from a Gaussian process, our methods perform comparably to the Gaussian method.
For data settings with skew-$t$ marginals (settings 2 -- 5), we find significant improvement over the Gaussian method.
Furthermore in these data settings, we find the best performance occurs when the number of knots used in the method matches the number of knots used for data generation.
The non-thresholded methods tend to outperform the thresholded methods, but this is not surprising given that the data are generated directly from the model used in the method.
For the max-stable data, we see that for low-extreme quantiles, the Gaussian method performs better, for more extreme quantiles, the single-partition method, both thresholded and non-thresholded, perform significantly better than the Gaussian.
Finally, for setting 5, although the thresholded version of the single-partition model tends to perform the best across all of the extreme quantiles, the difference between the thresholded and non-thresholded methods is no longer significant in the more extreme quantiles.

>>>>

\subsection{Extremal dependence}
Our interest lies in spatial dependence in the tail of the skew-$t$ process.
One measure of extremal dependence is the $\chi$ statistic \citep{Padoan2011}.
For a stationary and isotropic spatial process, the $\chi$ statistic for two location $\bs$ and $\bt$ separated by distance $h = || \bs - \bt ||$ is
\begin{align}
  \chi(h) = \lim_{c \rightarrow \infty} \Pr[Y(\bs) > c | Y(\bt) > c].
\end{align}
If $\chi(h) = 0$, then observations are asymptotically independent at distance $h$.
For Gaussian processes, $\chi(h) = 0$ regardless of the distance, so they are not suitable for modeling spatially-dependent extremes.
Unlike the Gaussian process, the skew-$t$ process is asymptotically dependent.
However, one problem with the spatial skew-$t$ process is that $\lim_{h \rightarrow \infty} \chi(h) > 0$ (see Appendix \ref{a:skewt} for a proof).
This occurs because all observations, both near and far, share the same $z$ and $\sigma$ terms.
Therefore, this long-range dependence feature of the skew-$t$ process is not ideal for spatial analysis of large geographic regions where we expect only local spatial dependence.
The explicit expression for $\chi(h)$ is given in Appendix \ref{a:skewt}.

@@

\subsection{Censoring to focus on the tails}
To avoid bias in estimating tail parameters, we model censored data.
Let
\beq\label{Yt}
  \widetilde{Y}(\bs) = \left\{ \begin{array}{ll}
      Y(\bs) \quad & \delta(\bs) = 1 \\
      T & \delta(\bs) = 0
  \end{array} \right.
\eeq
be the censored observation at site $\bs$ where $Y(\bs)$ is the uncensored observation, $\delta(\bs) = I[Y(\bs) > T]$, and $T$ is a pre-specified threshold value.
Then, assuming the uncensored data $Y(\bs)$ are observations from a skew-$t$ process, we update values censored below the threshold using standard Bayesian missing data methods as described in Section \ref{s:comp}.

\subsection{Partitioning to remove long-range asymptotic dependence}\label{s:part}
We handle the problem of long-range asymptotic dependence with a random partition.
As discussed in Section \ref{s:spatialskew}, the source of long-range dependence is the shared $z$ and $\sigma$.
Therefore, to alleviate this dependence, we allow $z$ and $\sigma$ to vary by site.
The model becomes
\begin{align} \label{eq:partition}
  Y(\bs) &= \bX(\bs)^T \bbeta + \lambda \sigma(\bs) |z(\bs)| + \sigma(\bs) v(\bs).
\end{align}
Let $\bw = (w_1, w_2)$ be the location of a spatial knot.
To model spatial variation, consider a set of spatial knots $\bw_1, \ldots, \bw_K$ from a homogeneous Poisson process with intensity $\mu$ over spatial domain $\calD \in \calR^2$.
The knots define a random partition of $\calD$ by subregions $P_{1}, \ldots, P_{K}$ defined as
\begin{align} \label{eq:subregions}
  P_{k} = \{ \bs : k = \argmin_\ell || \bs - \bw_{\ell} || \}.
\end{align}
All $z(\bs)$ and $\sigma(\bs)$ for sites in subregion $k$ are assigned common values
\begin{align}
  z(\bs) = z_{k} \quad \text{and} \quad \sigma(\bs) = \sigma_{k} \label{eq:sitezsig}
\end{align}
and the $z_k$ and $\sigma^2_k$ are distributed as $z_k \iid N(0, 1)$ and $\sigma^2 \iid$ IG$(a, b)$ where IG is the distribution function of an inverse gamma random variable.
So, within each partition, $Y(\bs)$ follows the spatial skew-$t$ process defined in Section \ref{s:spatialskew}.
Across partitions, the $Y(\bs)$ remain correlated via the correlation function for $v(\bs)$ because $v(\bs)$ spans all partitions.

When incorporating the random partition, conditional on knots $\bw_1, \ldots, \bw_K$, the $\chi$ statistic for two sites $\bs$ and $\bt$ in partitions $k_s$ and $k_t$ respectively is
\begin{align}
  \chi(h) &= I(k_s = k_t) \chi_{\text{skew-}t}(h) + I(k_s \neq k_t) \chi_{\text{Gaus}}(h) \nonumber \\
         &= I(k_s = k_t) \chi_{\text{skew-}t}(h)
\end{align}
where $I(\cdot)$ is an indicator function, $\chi_{\text{skew-}t}(h)$ is the $\chi$ statistic for a skew-$t$ process, $\chi_{\text{Gaus}}(h)$ is the $\chi$ statistic for a Gaussian process, and $h = ||\bs - \bt||$.
Therefore, sites in different subregions are asymptotically independent because $\chi_{\text{Gaus}}(h) = 0$ for all $h$.
Marginally, over the knots $\bw_1, \ldots, \bw_K$, $\chi(h) = \pi(h) \chi_{\text{skew}-t}(h)$, where $\pi(h) = \Pr(k_s = k_t)$ is the probability that two sites separated by distance $h$ are in the same partition.
So, to show that $\lim_{h \rightarrow \infty} \chi(h) = 0$, we need only know that $\lim_{h \rightarrow \infty} \pi(h) = 0$. A proof of this is given in Appendix \ref{a:proofsamepartition}.

In Figure \ref{fig:chi}, we give $\chi(h)$ for $K = 1, 3, 5, 10$ partitions for a skew-$t$ distribution with $\alpha = 10$, and 3 degrees of freedom.
To estimate $\pi(h)$, we generate 500 sites uniformly over the unit-square.
We then randomly generate 400 different sets of partitions using $K = 3$, $5$, and $10$.
For each set of knots, we take $\pi(h)$ to be the proportion of sites in the same partition that are separated by distance $h$.
This plot demonstrates how partitioning helps to reduce extremal dependence as $h$ increases.

@@

We use an AR(1) time series model for $w_{tk}$, $z_{tk}$, and $\sigma_{tk}$.
The time series model must be specified after a transformation to preserve the skew-$t$ process at each time point.
For each time-varying parameter, we transform to obtain a standard normal marginal distribution, place a Gaussian prior with autocorrelation on the transformed parameter, and then transform back to obtain the marginal distribution required to preserve the skew-$t$ process.
We first transform the spatial knots from $\calD$ to $\calR^2$ as follows.
Let
\begin{align}
  w^*_{tki} = \Phi^{-1}\left[ \frac{ w_{tki} - \min(\bs_i)}{ \max(\bs_i) - \min(\bs_i) } \right], \quad i = 1, 2
\end{align}
where $\Phi$ is a univariate standard normal density function, and $\bs_i = [s_{1i}, \ldots, s_{ni}]$.
Then the transformed knots $\bw^*_{tk} \in \calR^2$.
We use a copula on $\sigma^2_t(\bs)$ to ensure that the marginal distributions of $\sigma^2_t(\bs)$ are inverse gamma.
Let
\begin{align}
  \sigma^{2*}_t(\bs) =\Phi^{-1}\left\{ \text{IG}[\sigma^2_t(\bs)] \right\}
\end{align}
where IG is defined as before.
We also use a copula on $z_{t}(\bs)$ to ensure that the marginal distributions of $z_t(\bs)$ are half-normal.
Let
\begin{align}
  z^*_t(\bs) = \Phi^{-1}\left\{ \text{HN}[z_t(\bs)] \right\}
\end{align}
where HN is the distribution function of a half-normal random variable.
The AR(1) process for each tail parameter is $\bw^*_{1k} \sim N_w(0, 1)$, $z^*_{1k} \sim N(0, \sigma^2_{1k})$, $\sigma^{2*}_{1k} \sim N(0, 1)$, and for $t > 1$ the time series is modeled as
\begin{align}
  \bw^*_{tk} | \bw^*_{t-1, k} &\sim N_2\left[\phi_w \bw^*_{t-1, k}, (1 - \phi_w^2) \right] \\
  z^*_{tk} | z^*_{t-1, k} &\sim N \left[\phi_z z^*_{t-1, k}, \sigma^2_{tk} (1 - \phi_z^2)\right] \\
  \sigma^{2*}_{tk} | \sigma^{2*}_{t-1, k} &\sim N \left[\phi_\sigma \sigma^{2*}_{t-1, k}, (1 - \phi_\sigma^2) \right]
\end{align}
where $|\phi_w|$, $|\phi_z|$, $|\phi_\sigma| < 1$.
These are stationary time series models with marginal distributions \hbox{$\bw^*_{k} \sim N_2(0, 1)$}, \hbox{$z^*_{k} \sim N(0, \sigma^2_{k})$}, and \hbox{$\sigma^{2*}_{k} \sim N(0, 1)$}.
After transformation back to the original space, $\bw_{tk} \sim \text{Unif}(\calD)$, $z_{tk} \sim HN(0, \sigma^2_{tk})$ $\sigma^2_{tk} \sim \text{IG}(a, b)$.
For each day, the model is identical to the spatial-only model in (\ref{eq:partition}) by construction.

\section{Computation}\label{s:comp}
First, we impute values below the threshold.
Then, we update model parameters, $\Theta$, using Metropolis Hastings or Gibbs sampling when appropriate.
Finally, we make spatial predictions using conditional multivariate normal results and the fact that the distribution of $Y_t(\bs) \mid \Theta, z(\bs)$ is the usual multivariate normal distribution with a \Matern spatial covariance structure.

We can use Gibbs sampling to update $Y_t(\bs)$ for censored observations that are below the threshold $T$.
After conditioning on $\lambda$, $z_t(\bs)$ and non-censored observations, $Y_t(\bs)$ has truncated normal full conditionals.
So we sample $Y_t(\bs) \sim N_{(-\infty, T)}(\bX_t^T(\bs) \beta + \lambda | z_t(\bs)|, \bSigma)$.
After imputing the censored observations, we update the model parameters.
To update the model parameters, we use standard Gibbs updates for parameters when possible.
In the case Gibbs sampling is not possible, parameters are updated using a random-walk Metropolis Hastings algorithm.
See Appendices A.1 and A.2 for details regarding the MCMC.
The final step of the computation is to use Bayesian Kriging to generate a predictive distribution for $Y_t(\bs^*)$ at prediction location $\bs^*$.
This step is similar to the imputation for censored observations except that the full conditionals are no longer truncated at $T$.

\subsection{Hierarchical model}\label{s:hier}
Conditioned on $z_{tk}(\bs)$, $\sigma^2_{tk}(\bs)$, and $P_{tk}$, the marginal distributions are Gaussian and the joint distribution multivariate Gaussian.
However, we do not fix the partitions, they are treated as unknown and updated in the MCMC.
We model this with a Bayesian hierarchical model as follows.
Let $\bw_{t1}, \ldots, \bw_{tK}$ be a set of daily spatial knots in a spatial domain of interest, $\calD$, and $P_{tk}$ as defined in (\ref{eq:subregions}).
Then
\begin{align}
   Y_t(\bs) \mid z_{t}(\bs), \sigma_t^2(\bs), P_{tk}, \Theta &= \bX_t(\bs)^T \beta + \lambda |z_t(\bs)| + \sigma_t(\bs) v_t(\bs) \label{eq:hier}\\
   z_t(\bs) &= z_{tk} \text{ if } \bs \in P_{tk}\nonumber\\
   \sigma^2_{t}(\bs) &= \sigma^2_{tk} \text{ if } \bs \in P_{tk}\nonumber\\
   \lambda &= \lambda_1 \lambda_2\nonumber\\
   \lambda_1 &= \left\{ \begin{array}{ll}
      +1 \quad & \text{w.p. } 0.5\\
      -1 \quad & \text{w.p. } 0.5
   \end{array}\right.\nonumber\\
   \lambda^2_2 & \sim IG(a, b)\nonumber\\
   v_t(\bs) \mid \Theta &\sim \Matern(0, \Sigma)\nonumber\\
   z^*_{tk} \mid z^*_{t-1, k}, \sigma^2_{tk} &\sim N(\phi_z z^*_{t-1, k}, \sigma^2_{tk} (1 - \phi_z^2))\nonumber\\
   \sigma^{2*}_{tk} \mid \sigma^{2*}_{t-1, k} &\sim N(\phi_\sigma \sigma^{2*}_{t-1, k}, (1 - \phi_\sigma^2))\nonumber\\
   \bw^*_{tk} \mid \bw^*_{t-1, k} &\sim N_2(\phi_w \bw^*_{t-1, k}, (1 - \phi_w^2)) \nonumber
\end{align}
where $\Theta = \{\rho, \nu, \gamma\, \lambda, \beta\}$, and $\Sigma$ is a \Matern covariance matrix as described in Section \ref{s:skewt}.
We parameterize $\lambda = \lambda_1 \lambda_2$ to help with convergence in the MCMC.

@@

\subsection{Design}\label{s:simdesign}
For all simulation designs, we generate data from the model in Section \ref{s:part} using $n_s=144$ sites and $n_t=50$ independent days.
The sites are generated Uniform$([0, 10] \times [0, 10])$.
We generate data from 5 different simulation designs:
\begin{enumerate} \setlength{\itemsep}{-0.5em}
  \item Gaussian marginal, $K=1$ knot
  % \item Symmetric-$t$ marginal, $K=1$ knot
  % \item Symmetric-$t$ marginal, $K=5$ knots
  \item Skew-$t$ marginal, $K=1$ knots
  \item Skew-$t$ marginal, $K=5$ knots
  \item Max-stable
  \item Transformation below $T = q(0.80)$
\end{enumerate}
In the first three designs, the $v_t(\bs)$ terms are generated using a \Matern covariance with smoothness parameter $\nu = 0.5$ and spatial range $\rho = 1$.
For the covariance matrices in designs 1 -- 3, the proportion of the variance accounted for by the spatial variation is $\gamma = 0.9$ while the proportion of the variance accounted for by the nugget effect is $0.1$.
In the first design, $\sigma^2 = 2$ is used for all days which results in a Gaussian distribution.
For designs 2 and 3, $\sigma^2_{tk} \iid \text{IG}(3, 8)$ to give a $t$ distribution with 6 degrees of freedom.
For designs 1, we set $\lambda = 0$.
For designs 2 and 3, $\lambda = 3$ was used as to simulate moderate skewness, and the $z_t$ are generated as described in (\ref{eq:sitezsig}).
In the fourth design, we generate from a spatial max-stable distribution \citep{Reich2012}.
In this design, data have marginal distributions that follow a generalized extreme value distribution with parameters $\mu = 1, \sigma=1, \xi=0.2$.
In this model, a random effect is used to induce spatial dependence using 144 spatial knots on a regular lattice in the square $[1, 9] \times [1, 9]$.
For this setting, we set $\gamma = 0.5$.
In the final design, we generate $\tilde{y}$ using the setting from design two, and then consider the data
\begin{align}
  y = \left\{ \begin{array}{lc}
    \tilde{y}, \quad & \tilde{y} > T \\[0.5em]
    T \exp\{\tilde{y} - T\}, \quad & \tilde{y} \le T
  \end{array}\right.
\end{align}
where $T = q(0.80)$ is the 80th sample quantile of the data.
In all five designs, the mean $\bX^T \bbeta = 10$ is assumed to be constant across space.

$M = 50$ data sets are generated for each design.
For each data set we fit the data using five models
\begin{enumerate} \setlength{\itemsep}{-0.5em}
  \item Gaussian marginal, $K=1$ knots
  \item Skew-$t$ marginal, $K=1$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=1$ knots, $T=q(0.80)$
  \item Skew-$t$ marginal, $K=5$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=5$ knots, $T=q(0.80)$
\end{enumerate}
where $q(0.80)$ is the 80th sample quantile of the data.
The design matrix $\bX$ includes an intercept with a first-order spatial trend with priors of $\beta_\text{int}$, $\beta_\text{lat}$, $\beta_\text{long},  \iid \text{N}(0, 10)$.
The spatial covariance parameters have priors $\log(\nu) \sim \text{N}(-1.2, 1)$, $\gamma \sim \text{Unif}(0, 1)$, $\rho \sim \text{Unif}(15)$.
The skewness parameter has prior $\lambda_2 \sim \text{IG}(0.1, 0.1)$.
The residual variance terms have priors $\sigma^2_t(\bs) \sim \text{IG}(0.1, 0.1)$.
The knots have priors $\bw \sim \text{Unif}(\calD)$.
We do not include skewness for the thresholded models because it cannot be identified with only one tail worth of data, and we do not fit the data using the max-stable methods from \citet{Reich2012} because of the computational constraints.
Each chain of the mcmc ran for 20000 iterations with a burn-in period of 10000 iterations.
Parameters appear to converge properly; however, in the models with multiple partitions (i.e.models 4 and 5) it is hard to assess the convergence of $\bw$, $z(\bs)$, and $\sigma^2(\bs)$ because of partition label switching throughout the MCMC.

@@

Figure \ref{fig:simbrierscores} shows that when the data come from a Gaussian process, our methods perform comparably to the Gaussian method.
For data settings with skew-$t$ marginals (settings 2 -- 3), we find significant improvement over the Gaussian method.
Furthermore in these data settings, we find the best performance occurs when the number of knots used in the method matches the number of knots used for data generation.
The non-thresholded methods tend to outperform the thresholded methods, but this is not surprising given that the data are generated directly from the model used in the method.
For the max-stable data, we see that for low-extreme quantiles, the Gaussian method performs better, for more extreme quantiles, the single-partition method, both thresholded and non-thresholded, perform significantly better than the Gaussian.
Finally, for setting 5, although the thresholded version of the single-partition model tends to perform the best across all of the extreme quantiles, the difference between the thresholded and non-thresholded methods is no longer significant in the more extreme quantiles.
